---
output:
  pdf_document: default
  html_document: default
---

# Perform linear regression on climate dataset

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(error = TRUE,comment=NA) 
```


```{r libraries, include=FALSE}
# Load required libraries
library(kableExtra) # for nice tables

library(readxl) # for reading in an excel file

library(dplyr)

library(lubridate) # for handling date / time variables
library(ggplot2)

library(MASS)

# options for descriptive statistics
library(summarytools) # 
library(psych)

library(patchwork) # for plot layout options


library(corrplot) # correlation plots
library(performance) # regression model performance and comparison
# note that the compare_performance function also requires the see package installed.


library(glmnet) # for LASSO /  Ridge regression.
```

# Data description

This data was collected from Uk met office open source data

it contains the following variables:

- Year and month

- Mean daily temperature ('tmax degC' and 'tmin degC')

- Days of air frost ('af hours')

- Total rainfall ('rain mm')

- Total sunshine duration ('sun hours')

```{r data}
# load dataset
data<-read.csv("Scotland.csv")
head(data)
```


```{r dataprep}
# View data structure for more insight (variables)
str(data)
```
# Simple linear regression using oxford dataset

plot tmax.degC against tmin.degC


```{r}

#library(ggplot2)
ggplot(data, aes(y=tmax.degC,x=tmin.degC)) +
  geom_point()
```
we can deduce that when tmax.degC is high, tmin.degC is low
Is this simple linear regression good?


```{r}

with(data, cor(tmax.degC,tmin.degC))
with(data, cor.test(tmax.degC,tmin.degC))

```

